### 2020-01-29 Common/chapters/deep_learning.tex
Johan and Julien: Bibliography generated by Zotero

\subsection{Historical background}
\label{historical_background}
As described on figure \ref{history}, the theoretical foundations of deep learning appeared long before the invention of computers. From the first attempts to understand the human brain until today, huge progres was made to be establish the basic components of modern neural networks. One could ask why deep learning took off recently if the theory was around for a long time.\\
As stated by Goodfellow et al. \cite{15}, the first part of the answer is computing power. In fact, deep learning algorithms need a lot of data to work properly, which requires powerful CPUs/GPUs that either didn't exist or were only within few people's reach. One other main reason concerns the lack of data. Since deep learning algorithms "learn" from data, learning is impossible if good-quality data are not available. The era of Big Data enhanced deep learning possibilities. 
%%%% Je mettrais soit l'un soit l'autre. Le paragraphe du dessus c'est le paragraphe du dessous avec des autres mots :)
% These two points are summarised: "The increase in model size overtime, due to the availability of faster CPUs, the advent of general purpose GPUs, fasternetwork, connectivity and better software infrastructure for distributed computing, is one of the most important trends in the history of deep learning. This trend is generally expected to continue well into the future".\\
Finally, before the year 2012, the abilities of neural networks were still to be proven. This changed with the ImageNet Large Scale Visual Recognition Challenge (a competition where researchers evaluate their algorithms on several visual recognition tasks). In fact, the deep convolutional neural network called "AlexNet" achieved 16\% of classification error rate, whereas the previous best scores were around 25\%. This victory marked the beginning of a new craze for these types of algorithms.

@@

\subsection{Supervised and unsupervised learning}
In machine learning, two different kinds of tasks exist. The first one is "supervised learning". It includes learning algorithms whose training samples are associtted to their labels in order to find the optimal mapping between the input and the output. The second one is "unsupervised learning". In contrast to supervised algorithms, the latter rely on unlabeled data. Its main goal is to infer the natural structure  present in the data. Since the models presented in this work belong to the "supervised learning" category, notions explained below refer to this kind of algorithms.

>>>>

\subsection{Historical background}
\label{historical_background}
As described on figure \ref{history}, the theoretical foundations of deep learning appeared long before the invention of computers. From the first attempts to understand the human brain until today, huge progress was made to be establish the basic components of modern neural networks. One could ask why deep learning took off recently if the theory was around for a long time.\\
As stated by Goodfellow et al. \cite{15}, the first part of the answer is computing power. In fact, deep learning algorithms need a lot of data to work properly, which requires powerful CPUs/GPUs that either didn't exist or were only within few people's reach. One other main reason concerns the lack of data. Since deep learning algorithms "learn" from data, learning is impossible if good-quality data are not available. The era of Big Data enhanced deep learning possibilities. 
%%%% Je mettrais soit l'un soit l'autre. Le paragraphe du dessus c'est le paragraphe du dessous avec des autres mots :)
% These two points are summarised: "The increase in model size overtime, due to the availability of faster CPUs, the advent of general purpose GPUs, fasternetwork, connectivity and better software infrastructure for distributed computing, is one of the most important trends in the history of deep learning. This trend is generally expected to continue well into the future".\\
Finally, before the year 2012, the abilities of neural networks were still to be proven. This changed with the ImageNet Large Scale Visual Recognition Challenge (a competition where researchers evaluate their algorithms on several visual recognition tasks). In fact, the deep convolutional neural network called "AlexNet" achieved 16\% of classification error rate, whereas the previous best scores were around 25\%. This victory marked the beginning of a new craze for these types of algorithms.

@@

\subsection{Supervised and unsupervised learning}
In machine learning, two different kinds of tasks exist. The first one is "supervised learning". It includes learning algorithms whose training samples are associated to their labels in order to find the optimal mapping between the input and the output. The second one is "unsupervised learning". In contrast to supervised algorithms, the latter rely on unlabeled data. Its main goal is to infer the natural structure  present in the data. Since the models presented in this work belong to the "supervised learning" category, notions explained below refer to this kind of algorithms.
